---
title: "DSCI 30100: Lesson 01"
output: html_notebook
---

# Setup

```{r}
# Data
library(AER)

# Manipulation
library(dplyr)

# Visualization
library(ggplot2)
```

# Import: Impact of Beauty on Instructor's Teaching Ratings

  * Hamermesh, D.S., and Parker, A. (2005). Beauty in the Classroom: Instructors' Pulchritude and Putative Pedagogical Productivity. Economics of Education Review, 24, 369-376.
  * [See CRAN:](https://cran.r-project.org/web/packages/AER/AER.pdf), page 164-165.

## Data

Data on course evaluations, course characteristics, and professor characteristics for 463 courses for the academic years 2000-2002 at the University of Texas at Austin. A sample of student instructional ratings for a group of university teachers along with beauty rating (average from six independent judges) and a number of other characteristics. The data were provided by Prof. Hamermesh.

  * __minority__: (factor) Does the instructor belong to a minority (non-Caucasian)?
  * __age__:               The professor's age.
  * __gender__: (factor)   Indicating instructor's gender.
  * __credits__: (factor)  Is the course a single-credit elective (e.g., yoga, aerobics, dance)?
  * __beauty__:            Rating of the instructor's physical appearance by a panel of six students, averaged across the six panelists, shifted to have a mean of zero.
  * __eval__:              Course overall teaching evaluation score, on a scale of 1 (very unsatisfactory) to 5 (excellent).
  * __division__: (factor) Is the course an upper or lower division course? (Lower division courses are mainly large freshman and sophomore courses)?
  * __native__: (factor)   Is the instructor a native English speaker?
  * __tenure__: (factor)   Is the instructor on tenure track?
  * __students__:          Number of students that participated in the evaluation.
  * __allstudents__:       Number of students enrolled in the course.
  * __prof__: (factor)     Indicating instructor identifier.


```{r}
data("TeachingRatings")
```

# First Steps

```{r}
TeachingRatings
```

```{r}
summary(TeachingRatings)
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty))
```

## Exercise Examples

```{r}
ggplot(data = TeachingRatings)
```

# Aesthetic Mapping

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, colour = gender))
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, size = students))
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, alpha = students))
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, shape = gender))
```


```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, shape = gender))
```


```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, shape = gender), colour = "cornflowerblue")
```

## Exercise Examples

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty, colour = "cornflowerblue"))
```

# Common Problems

```{r}
ggplot(data = TeachingRatings)
  + geom_point(mapping = aes(x = age, y = beauty))
```

# Facets

```{r}
ggplot(data = TeachingRatings) + 
  geom_point(mapping = aes(x = age, y = beauty)) + 
  facet_wrap(~ native)
```

# Geometric Objects

```{r}
ggplot(data = TeachingRatings) + 
  geom_smooth(mapping = aes(x = age, y = beauty))
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_smooth(mapping = aes(x = age, y = beauty)) + 
  geom_point(mapping = aes(x = age, y = beauty))
```

```{r}
ggplot(data = TeachingRatings) + 
  geom_smooth(mapping = aes(x = age, y = beauty, colour = gender)) + 
  geom_point(mapping = aes(x = age, y = beauty, colour = gender))
```

# Function Short Cuts

```{r}
ggplot(TeachingRatings, aes(age, beauty, colour = gender)) + 
  geom_smooth() + 
  geom_point()
```


# Just For Fun

```{r}
lm(eval ~ beauty + age + minority + gender + tenure + division, TeachingRatings) %>% 
  summary()
```

